---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CdaPrac1

<!-- badges: start -->
<!-- badges: end -->

CdaPrac1 is an educational R package designed to help students understand and implement
Coordinate Descent Algorithms (CDA), particularly for the Lasso regression.

This package provides:

A pure R implementation of Lasso via Coordinate Descent

A fast Rcpp-based version (lasso_cda_cpp)

A user-friendly wrapper (lasso_cda) that performs
automatic standardization, coefficient recovery, and intercept calculation

Clean examples for learning and benchmarking

## Installation

You can install the development version of CdaPrac1 from GitHub:


``` r
# install.packages("pak")
pak::pak("LJWstat/CdaPrac1")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(CdaPrac1)
# 
# set.seed(1)
# 
# # Simulated data
# 
# n <- 100
# p <- 10
# X <- matrix(rnorm(n*p), n, p)
# beta_true <- c(3, -2, rep(0, 8))
# y <- X %*% beta_true + rnorm(n)
# 
# # Fit Lasso using CDA (R + Rcpp implementation)
# 
# fit <- lasso_cda(X, y, lambda = 0.5)
# 
# fit$beta       # estimated coefficients
# fit$intercept  # estimated intercept
```

### Benchmark: R vs Rcpp

```{r example2}
# library(microbenchmark)
# 
# fit_r <- function() lasso_cda_r(X, y, lambda = 0.5)
# fit_cpp <- function() lasso_cda_cpp(X, y, 0.5)
# 
# microbenchmark(
# R = fit_r(),
# Rcpp = fit_cpp(),
# times = 20
# )
```

### Plot Example

```{r example3}
# grid <- seq(-1, 1, length.out = 200)
# 
# plot(grid, grid^2, type = "l",
# main = "Example Plot (replace with real Lasso visualization)",
# col = "steelblue", lwd = 2)
```

